\documentclass[main.tex]{subfiles}
\begin{document}

\paragraph{Feature: Pop-up}
\begin{itemize}
	\item Desly
		\begin{itemize}
			\item Can point out important info so you can remember it better.
			\item Possibly pop-up spam when you scroll through.
		\end{itemize}
	\item Jimmy
		\begin{itemize}
			\item Extra information helps learning.
			\item Can be a distraction.
		\end{itemize}
	\item Ingrid
		\begin{itemize}
			\item Only usefull if a teacher does it, author should just put some extra facts or a note in the text
			\item Helps with learning
		\end{itemize}
	\item Tamar
		\begin{itemize}
			\item Annoying if there are multiple pop-ups at the same time.
			\item Helps with putting your attention to what is important.
		\end{itemize}

\end{itemize}

\paragraph{Feature: Graph}
\begin{itemize}
	\item Desly
		\begin{itemize}
			\item Realtime feedback
			\item Easier to see relations between values and representation
			\item (Does this only work for linear graphs?)
			\item (Can you only change the graph and see the values change or also the values so the graph changes?)
		\end{itemize}
	\item Jimmy
		\begin{itemize}
			\item Interaction helps understanding.
		\end{itemize}
	\item  Ingrid
		\begin{itemize}
			\item Helps to understand the behaviour of a formula
 			\item should not be able to do this if it are research results / statistics, they should not be changed. 
		\end{itemize}
	\item Tamar
		\begin{itemize}
			\item Can be usefull with difficult formulas, see what happens when values are added or something.
		\end{itemize}
\end{itemize}

\paragraph{Feature: Perspective}
\begin{itemize}
	\item Desly
		\begin{itemize}
			\item Definition view could provide more detail and image view more a global idea.
			\item Freedom to choose your reading style.
		\end{itemize}
	\item Jimmy
		\begin{itemize}
			\item (Can you swap at any time?)
			\item Different views creates a diverse and less boring experience.
			\item Natural in use; you use different representations for different things.
			\item Maybe not all information can be properly defined in both formats.
			\item Swapping between views could make reading hard/cluttered.
		\end{itemize}
	\item Ingrid
		\begin{itemize}
			\item Helps with different learning styles
			\item You have to be able to swap between perspectives at any time. 
		\end{itemize}
	\item Tamar
		\begin{itemize}
			\item Can you also mix perspectives? If I like definitions and images?
			\item Easy to adjust to my reading style.
		\end{itemize}
 	
\end{itemize}

\end{document}
