\documentclass[Main.tex]{subfiles} 


\begin{document}
The participants in the prototyping session are of vital importance. Their backgrounds will determine the kind of feedback there will come out of the session. Two categories of participants will most likely not give usefull feedback. These are:

\begin{itemize}
\item Insiders. Participants that already have a stake in the product
\item Fanboys/girls. Participants that already like the product, because of the company or any other particulair reason.
\end{itemize}
The insiders are bad participants because they are biased. They can only observe the inside view. Kahneman states the exact problem on the inside view: \\ \\
\emph{He's taking an inside view. He should forget about his own case and look for what happened in other cases.} \\ \\
In a prototype session all the cases of the inside view are probably already covered by the prototype however the outside view will render cases that give usefull feedback. Having only insiders in the prototype session will thus hurt your feedback results.

The second group of participants is fanboys/fangirls. These participants will most likely fall for a different kind of fallacy, namely answering the easier question. Instead of looking at the product from an unbiased perspective they will like already like product. This is because, they replace the question \emph{How much do I like this prototype?} with an easier question: \emph{How much do I like the company or their earlier products?}. This based perspective will negatively influence their ability to find new cases or flaws in the prototype.
\end{document}